### 2015-01-14 publishing/plos_template.tex
intro updated to uTAs final
oppegard citetation fixed

3D printing of microfluidic devices enables rapid, one-step fabrication of complex designs infeasible to make with planar lithography and replica molding techniques.
In addition, planar lithography is time consuming, requires specialized equipment and facilities, and has a high failure rate.
On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which is outsourced to a 3D printing company for around \$100/device \cite{Au2014,Chen2014}.
Recently 3D printing has emerged as a method for directly printing complete microfluidic devices (folch, spence, that other one). 
Printing is currently limited in choice of materials when compared to MEMS style fabrication. 
As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials.
Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.

This is a test of the citations \cite{oppegard2010}.

@@

The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work\cite{Oppegard2010} and also incorporates integrated hose barbs.
The pillars extend into each well leaving a $/sim$500 $\mu$m gap for media between the diffusion membrane and the culutre surface at the bottom of the well.
Diffusion occurs rapidly across this gap allowing control of the dissolved gas environment around the cells. 
This is a prototype intended to be expanded to control all 24 wells.
A distribution network stems from the central input that equalizes the flow along each path length by varying the channel width to the proximal, intermediate, and distal wells.
The device also features a ‘pipe within a pipe’ design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing (Figure \ref{fgr:well-render}.
A PDMS membrane is adhered to the microchannels of both designs by spin coating a thin PDMS layer as an adhesive.

>>>>

3D printing of microfluidic devices enables rapid, one-step fabrication of complex designs infeasible to make with planar lithography and replica molding techniques.
In addition, planar lithography is time consuming, requires specialized equipment and facilities, and has a high failure rate.
On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which is outsourced to a 3D printing company for around \$100/device \cite{Au2014,Chen2014}.
Recently 3D printing has emerged as a method for directly printing complete microfluidic devices (folch, spence, that other one). 
Printing is currently limited in choice of materials when compared to MEMS style fabrication. 
As of yet there is no widely available methods or materials to facilitate direct printing of gas permeable materials.
Here we report on the development of 3D printed microfluidic devices for the control of oxygen in cell culture microenvironments.
Two devices are demonstrated: an open-well petri dish design and a device that nests into a 24 well culture plate.

@@

The 24 well plate insert is designed to control gas in 6 wells of a 24 well culture plate from one input, borrowing the working principle of previous work\cite{oppegard2010} and also incorporates integrated hose barbs.
The pillars extend into each well leaving a $/sim$500 $\mu$m gap for media between the diffusion membrane and the culutre surface at the bottom of the well.
Diffusion occurs rapidly across this gap allowing control of the dissolved gas environment around the cells. 
This is a prototype intended to be expanded to control all 24 wells.
A distribution network stems from the central input that equalizes the flow along each path length by varying the channel width to the proximal, intermediate, and distal wells.
The device also features a ‘pipe within a pipe’ design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing (Figure \ref{fgr:well-render}.
A PDMS membrane is adhered to the microchannels of both designs by spin coating a thin PDMS layer as an adhesive.
